Luminance constancy under fixed geometry

### 2018-03-07 Draft2/draft2.tex
Through the intro.  May need to meld some prose into methods, we’ll see.

Early work on computational color constancy considered a simplified case with multiple flat matte objects and a single spatially diffuse illuminant \citeNP{LandRetinex,Buchsbaum80,MaloneyWandell86}).
A key insight from this work is that stable color descriptors of a target object cannot be obtained from the light reflected from the target object alone.  But, it is possible to obtain such descriptors by analyzing jointly the light reflected from all of the objects in the scene.
As a consequence, the performance of color constancy algorithms will be affected by variation in the surface reflectance of all of the objects in the scene \cite{BrainardWandellRetinex}, not just by variation in the illuminant. Thus evaluation of constancy algorithms must include assessment of their performance with respect to both variation in the illumination and the surface reflectance of all of the scene objects.

*** HERE ***

At the same time, this processing introduces an additional dependence.  Although the reflectance of the objects surrounding an object of interest has little direct effect on the light reflected from the object of interest, variation in the reflectance of the surrounding objects can have a large effect on the output of constancy algorithms that process the entire image

Thus, a key aspect evaluating computational constancy algorithms is not only to ask about target object color stability with respect to variation in illumination, but also to ask about target object color stability with respect to the surface reflectance of other objects in the scene.

***
Subsequent work, which extended the analysis to include richer geometric descriptions and to incorporate probabilistic descriptions of the statistics of naturally occurring scenes \cite{funt1988color, D'ZmuraConstancy3, barron2012color, D'ZmuraIversonSinger,BrainardFreeman}; LET'S SEE IF WE CAN FIND SOME RECENT REVIEWS), confirmed this basic insight.

Seminal computational color constancy algorithms applied to a  considered a simplified case in which flat matte surfaces are illuminated by a single spatially diffuse illuminant and explored algorithms that could either recover a descriptor correlated with object surface reflectance (e.g. \citeNP{LandRetinex}) or produce explicit estimates of object surface reflectance and/or illuminant spectral power distribution (e.g., .
Subsequent computational constancy work sought to generalize both the image formation model   None-the-less, it is not known how best to estimate stable object descriptors from images of the natural scenes we view in daily life.

% Figure 1: Introduction
\begin{figure}
\centering
\begin{subfigure}{0.4 \textwidth}
		\centering
        \includegraphics[width=\textwidth]{../Figures/Figure1/Figure1_a.png}
        \caption{}
        \label{fig:introSchematic}
    \end{subfigure}
    \begin{subfigure}{0.45 \textwidth}   
        \includegraphics[width=\textwidth]{../Figures/Figure1/Figure1_b.jpeg}
        \caption{}
        \label{fig:introExampleFigure}
    \end{subfigure}
    \label{introFigure}
    \caption{(a) {\bf Color Constancy:} The light reflected from an object to the eye depends both on the surface reflectance of the object and the illumination spectrum of the light source. It also depends on geometric factors, such as the object's shape, pose, and position relative to the observer. The human visual system is able to account for variations in the reflected light due to such extrinsic factors and produce a percept of object color that is relatively stable with respect to such variations. Such invariant color perception is called color constancy. (b) {\bf Luminance Constancy Under Spectral Variations:} In this paper we consider the special case of luminance constancy. Fig.~\ref{fig:introExampleFigure} shows images of an object (the sphere in the center of each image) at three levels of object luminance (indicated on the left). Within each row, the surface reflectance of the spheres has the same luminance when illuminated by a standard reference illuminant, CIE D65. The three rows differ in this value, as can be seen by the fact that the luminance of the spheres generally decreases as we move down the columns. Within each row, the relative surface reflectance of the spheres varies, as can be seen by the variation in color appearance across the each row.  Within each column, this relative surface reflectance is held fixed. For illustration, we have kept the light source and the background objects fixed across the panels. See Fig.~\ref{fig:studiedCases} for images with such variations. In this paper, we seek to identify computations that accurately estimate object luminance across variations in relative surface reflectance, variations in illumination, and variation in the reflectance of other objects in the scene.}
 \end{figure}
 % REMOVE EQUATION FROM 1a. IT'S NOT DOING ANY WORK AND IT ISN'T ACCURATE IN 3D WHERE EVERYTHING IS MORE COMPLICATED.

The computational work reviewed above is based on formulating an explicit model of the image formation process and the statistical properties of natural images, and leveraging these formulations to obtain an appropriate ``inverse optics" algorithm.  An alternative approach, which has been less-well explored, is to use supervised machine learning techniques to develop mappings between input images and stable color descriptors.  Along these lines, Barron \cite{barron2015convolutional} recently developed a color balancing algorithm based on training a neural network to detect a uniform illuminant in an image by matching image templates in the chromaticity space. The use of supervised learning to understand human perceptual capabilities has enjoyed success in domains outside of color vision. Geisler and colleagues, for example, have developed a technique they refer to as accuracy maximization analysis (AMA, \citeNP{geisler2009optimal}), which learns linear filters whose output carries information that is optimized for particular perceptual tasks. This technique has provided computations that efficiently estimate speed \cite{burge2015optimal}, focus error \cite{burge2011optimal}, and disparity \cite{burge2014optimal} 
from image patches taken from natural scenes, and that in addition provide excellent models of human's ability to make corresponding estimates from the same stimuli.  In this paper, we apply AMA, as well as comparison supervised learning algorithms to a special case of the color constancy problem (luminance constancy) and evaluate how well it performs for naturalistic image input.

A difficulty in using machine learning approaches for color constancy is that these approaches require large training sets with images of scenes containing objects with known surface reflectances illuminated with known illuminations.  Such data sets are not readily available. Although there are several databases of calibrated color natural images, these do not generally provide the corresponding information about surface and illuminant ground truth \cite{ChakrabartiHyperspectral,NascimentoFoster2016,ParragaHyperspectralData,TkacikUpennHypersepctralData,skauli2013collection,olmos2004biologically}. 
Generating databases with both the images and the ground truth scene information is not trivial. One approach has been to acquire images where objects of known reflectance have been inserted into the scene, and to use the image of these reference objects to provide an estimate of the illumination impinging at various scene locations \cite{NascimentoFoster2016}.  This is somewhat painstaking, however, and in any case provides information about the illumination only at a small number of selected locations, so that generalizing across the image requires strong assumptions. Some progress is being made on characterizing how illumination varies over space in natural scenes \cite{mury2007spatial}, which in the longer run may guide how information from reference objects can be used to provide reasonable estimates.  Another approach is to acquire images of posed scenes, where the surface reflectances of objects are measured individually for many of the objects in the scene \cite{funt1988color,ciurea2003large, davidPennHyperspectral}. 
% REMOVE NO DATE (n.d.) FROM THE CITATION
These data sets have been useful for evaluating computational color constancy algorithms, but the use of posed scenes does not scale well for use with supervised learning methods which needs large training sets.

@@

Because of the difficulty in obtaining large labelled data sets of natural images for use in developing and evaluating computational color constancy algorithms, in this paper we adopt the approach of using high-quality computer graphics to render images of what we refer to as {\em virtual natural scenes}. Here, in addition to employing computer graphics to render the light reaching the eye from specified scenes, we also model the initial steps of the human visual system, so that our supervised learning methods are applied not to image pixels but rather to modeled responses of the foveal cone photoreceptor mosaic. We describe this approach in detail below. The key advantage of this approach is that we can produce large numbers of naturalistic images and the corresponding cone mosaic responses where all of the underlying scene properties are well-specified. This allows us to explore and evaluate computational color constancy with rich stimuli, while retaining the ability to precisely control and manipulate the intrinsic properties of the objects and illuminants that comprise the scene. This general approach has been adopted by other labs for the study of computational estimation of optical flow \cite{baker2011database} and is becoming increasingly popular \cite{kovacs17shading},
% Autonmous vehicle work - ask BAW
as well as for the generation of stimuli for the study of human perception (e.g., \citeNP{boyaci2003effect, todd1983perception, arend1986Simultaneous, johnston1993integration}). 
Of course, success within the domain of graphics images does not guarantee smooth generalization to real natural images, a point we return to in the \nameref{Discussion}.

>>>>

Early work on computational color constancy considered a simplified case with multiple flat matte objects and a single spatially diffuse illuminant \citeNP{LandRetinex,Buchsbaum80,MaloneyWandell86}). Subsequent computational considered more complex geometries and incorporated probabilistic descriptions of the statistics of naturally occurring scenes \cite{funt1988color, D'ZmuraConstancy3, barron2012color, D'ZmuraIversonSinger,BrainardFreeman}; LET'S SEE IF WE CAN FIND SOME RECENT REVIEWS).
A key insight from this computational work is that stable color descriptors of a target object cannot be obtained from the light reflected from the target object alone.  But, it is possible to obtain such descriptors by analyzing jointly the light reflected from all of the objects in the scene.
As a consequence, the performance of color constancy algorithms will be affected by variation in the surface reflectance of all of the objects in the scene \cite{BrainardWandellRetinex}, not just by variation in the illuminant. Thus evaluation of constancy algorithms must include assessment of their performance with respect to both variation in the illumination and the surface reflectance of all of the scene objects \cite{BrainardWandellRetinex,BrainardFreeman}.

% Figure 1: Introduction
\begin{figure}
\centering
\begin{subfigure}{0.4 \textwidth}
		\centering
        \includegraphics[width=\textwidth]{../Figures/Figure1/Figure1_a.png}
        \caption{}
        \label{fig:introSchematic}
    \end{subfigure}
    \begin{subfigure}{0.45 \textwidth}   
        \includegraphics[width=\textwidth]{../Figures/Figure1/Figure1_b.jpeg}
        \caption{}
        \label{fig:introExampleFigure}
    \end{subfigure}
    \label{introFigure}
    \caption{(a) {\bf Color Constancy:} The light reflected from an object to the eye depends both on the object's surface reflectance of the object and the illumination. It also depends on geometric factors, such as the object's shape, pose, and position relative to the observer. The human visual system is able to account for variations in the reflected light due to object-extrinsic factors and produce a percept of object color that is relatively stable, an ability called color constancy. (b) {\bf Luminance Constancy:} Images of a sphere under a fixed illuminant.  Down each column, the reflectance function of the sphere varies only by a scale factor; the relative reflectance spectrum held fixed.  The relative spectrum (shape of reflectance spectrum) varies across each row.
Within each row, the object luminance of the spheres is constant; we define object luminance as the luminance of the light that would be reflected by the object's surface under standard illuminant CIE D65.  The values on the left of each row provide the corresponding object luminance. We cast the problem of computational luminance constancy to be that of estimating object luminance from the image, across variation in other scene factors: variation in relative surface reflectance, variation in illumination, and variation in the reflectance of the other objects in the scene.}
 \end{figure}
 % REMOVE EQUATION FROM 1a. IT'S NOT DOING ANY WORK AND IT ISN'T ACCURATE IN 3D WHERE EVERYTHING IS MORE COMPLICATED.
 % MOVE (a) and (b) to upper left of each panel.
 % DELETE NUMBERS 1 to 5 at bottom of each row.

An alternative approach to computational color constancy, which has been less-well explored, is to use supervised machine learning techniques to develop mappings between input images and stable color descriptors \cite{barron2015convolutional}. The use of supervised learning to understand perceptual capabilities for natural stimuli has enjoyed success in domains outside of color vision. For example, a recently developed technique called accuracy maximization analysis (AMA) learns linear filters optimized for particular perceptual tasks \citeNP{geisler2009optimal}. It has been used to develop ideal observers for speed, focus error, and disparity estimation that provide excellent models of human performance \cite{burge2015optimal, burge2011optimal, burge2014optimal}. In this paper, we apply AMA to a special case of computational color constancy.

Supervised learning requires large labelled data sets.  Such data sets are not readily available for the study of color constancy. Although there are databases of calibrated color images, these do not provide ground truth information about surface reflectance and illuminantion at each image location \cite{ChakrabartiHyperspectral,NascimentoFoster2016,ParragaHyperspectralData,TkacikUpennHypersepctralData,skauli2013collection,olmos2004biologically}. There are some smaller databases consisting of images of posed scenes where object surface reflectances are measured individually \cite{funt1988color,ciurea2003large, davidPennHyperspectral}, but these are not large enough to drive supervised learning.

@@

In this paper, we use high-quality computer graphics to generate large data sets of naturalistic images where the surface reflectance and illumination corresponding to each image pixel are known. 
This approach allows us to investigate computational color constancy with naturalistic stimuli, while retaining the ability to control the properties of objects and illuminants. Here, we use this approach to tackle luminance constancy, a constitutive component of the more general color constancy problem (Fig.~\ref{fig:introExampleFigure}).

% MOVE ALL THIS TO DICUSSION
%This general approach has been adopted by other labs for the study of computational estimation of optical flow (Baker et al., 2011) and is becoming increasingly popular (Kovacs, Bell, Snavely, & Bala, 2017), as well as for the generation of stimuli for the study of human perception (e.g., Boyaci, Maloney, & Hersh, 2003; Todd & Mingolla, 1983; Arend & Reeves, 1986; Johnston, Cumming, & Parker, 1993). Of course, success within the domain of graphics images does not guarantee smooth generalization to real natural images, a point we return to in the Discussion.
% \cite{baker2011database}  \cite{kovacs17shading} \citeNP{boyaci2003effect, todd1983perception, arend1986Simultaneous, johnston1993integration}
% Autonmous vehicle work - ask BAW

 {\em virtual natural scenes}.

 we also model the initial steps of the human visual system, so that our supervised learning methods are applied not to image pixels but rather to modeled responses of the foveal cone photoreceptor mosaic.
